Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors That Have Mixed During Cooling

### 2019-06-12 paper/ms.tex
address comments in beginning of results section

We frame the presentation of the results of the suites of simulations
principally in terms of the yield of \Ni{56}, the energy source of
the light curve of an event. \Ni{56} thus serves as a proxy
for the brightness of an explosion and comparison of the yields
is equivalent to comparing the brightness of events. The
yields were estimated from $Y_e$ and the NSE progress
variable, by assuming the composition in NSE is \Ni{56} plus equal
parts \Fe{54} and \Ni{58}, as described in
\citet{townetal2009,Meaketal09}.

\begin{figure}
\includegraphics[width=\columnwidth]{figures/cum_dis_Ni56.pdf}
\caption{\label{fig:cumdist}
The cumulative distribution of the final \Ni{56} yield for explosions from
C-O and hybrid C-O-Ne models. The hybrid results are shown in red, and the CO
results are shown in blue. The curve for the hybrid models is shifted
to the left, indicating that explosions from hybrid progenitors produce
less \Ni{56} than explosions from traditional C-O models.
}
\end{figure}
The cumulative distribution of the \Ni{56} yield for explosions from
C-O and hybrid C-O-Ne models is presented in Figure \ref{fig:cumdist}.
The figure shows that the hybrid models consistently have a higher
cumulative fraction at a given mass of \Ni{56}, which indicates
that the yields of \Ni{56} are consistently lower in explosions
from hybrid progenitors. {\color{red} CHECK/EXPAND THIS}

\begin{figure}
\includegraphics[width=\columnwidth]{figures/Hybrid_Ni56mass_v_time_plot.pdf}
\caption{\label{fig:nithybrid}
Estimated \Ni{56} mass vs.\ time for ten hybrid model explosion simulations.
Shown are realizations 21-30.
}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{figures/CO_Ni56mass_v_time_plot.pdf}
\caption{\label{fig:nitco}
Estimated \Ni{56} mass vs.\ time for ten C-O model explosion simulations.
Shown are realizations 21-30.
}
\end{figure}

The estimated production of \Ni{56} as a function of simulation time
for 10 simulations of explosions from the hybrid progenitor is shown
in Figure \ref{fig:nithybrid} and from the traditional C-O progenitor is
shown in Figure \ref{fig:nitco}.
{\color{blue} The figures show that the final estimated \Ni{56} for
  the C-O model is slightly larger than the hybrid model. Therefore,
  the C-O produces more \Ni{56}. The hybrid model has a larger range
  then the C-O model. [Figure \ref{fig:nithybrid} and Figure
  \ref{fig:nitco} cannot support general claims like this because they
  only show ten of our realizations and it's hard to measure by
  eye. Figure \ref{fig:cumdist} is much better at demonstrating both
  of these statements.]}
Also, on average, the CO model reaches the DDT phase sooner then the
hybrid model.  Both figures show that production of \Ni{56}
effectively ceases (the curves flatten out) well before the end of the
simulations at $4.0$~\second. Also, the figures show that a few
simulations did not complete. {\color{red} OFFER A WHY?}

\blust{The degree of expansion was found using the time at which the first
detonation point occurred, and the mass at density greater than 2e7 g/cc. The
estimated \Ni{56} Yield is the final estimated mass of the model.}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/RatioNi56IGE_v_time_plot.pdf}
\caption{\label{fig:compare_ratio}
Plot of estimated \Ni{56} mass vs.\ time showing the evolution
for both suites of simulations. Results from
C-O-Ne progenitors are in red and C-O progenitors blue.
{\color{red} SAME AS DON'S FIGURE 19}.
%SAME AS DON'S FIGURE 19
}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{figures/MBTI_v_time_plot.pdf}
\caption{\label{fig:compare_burned}
Plot of estimated mass burned to IGEs vs.\ time showing the evolution
for both suites of simulations. Results from C-O-Ne progenitors are
in red and C-O progenitors blue.
Note that one of the C/O simulations presented did not complete.
%SAME AS DON'S FIGURE 20
{\color{red} SAME AS DON'S FIGURE 20.}
}
\end{figure}

>>>>

We frame the presentation of the results of the suites of simulations
principally in terms of the yield of \Ni{56}, the energy source of
the light curve of an event. \Ni{56} thus serves as a proxy
for the brightness of an explosion and comparison of the yields
is equivalent to comparing the brightness of events. The
yields were estimated from $Y_e$ and the NSE progress
variable, by assuming the composition in NSE is \Ni{56} plus equal
parts \Fe{54} and \Ni{58}, as described in
\citet{townetal2009,Meaketal09}.
This assumption allows the fraction of IGEs in the form of $^{56}$Ni to be estimated from the $Y_e$ tracked by the burning model.

\begin{figure}
\includegraphics[width=\columnwidth]{figures/cum_dis_Ni56.pdf}
\caption{\label{fig:cumdist}
The cumulative distribution of the final \Ni{56} yield for explosions from
C-O (red) and hybrid C-O-Ne (blue) models.
The curve for the hybrid models is shifted
to the left, indicating that explosions from hybrid progenitors produce
less \Ni{56} than explosions from traditional C-O models with the same central density.
}
\end{figure}
The cumulative distribution of the \Ni{56} yield for explosions from
C-O and hybrid C-O-Ne models is presented in Figure \ref{fig:cumdist}.
The figure shows that the hybrid models consistently have a higher
cumulative fraction at a given mass of \Ni{56}, which indicates
that the yields of \Ni{56} are consistently lower in explosions
from hybrid progenitors of the same central density.
This contrast is in a similar direction but not as large as the difference between C-O and C-O-Ne progenitors seen in W16.

{\color{red} TODO: make table of average yields (like table 1 in W16).}

\begin{figure}
\includegraphics[width=\columnwidth]{figures/Hybrid_Ni56mass_v_time_plot.pdf}
\includegraphics[width=\columnwidth]{figures/CO_Ni56mass_v_time_plot.pdf}
\caption{\label{fig:nithybrid} \label{fig:nitco}
Evolution of expected \Ni{56} yield in time for ten hybrid C-O-Ne WD (top panel) and ten C-O WD (bottom panel) explosion simulations.
Shown are realizations 21-30.
}
\end{figure}

The expected final production of \Ni{56} as a function of simulation time
for 10 simulations of explosions from each progenitor is shown in Figure \ref{fig:nithybrid}.
On average, the CO model reaches the DDT phase sooner then the
hybrid model.
A few simulations ended early, but after reaching their final yields, due to problematic physical conditions in the fluff.
{\color{red}TODO: confirm.}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/RatioNi56IGE_v_time_plot.pdf}
\caption{\label{fig:compare_ratio}
Plot of estimated \Ni{56} mass vs.\ time showing the evolution
for both suites of simulations. Results from
C-O-Ne progenitors are in red and C-O progenitors blue.
%SAME AS DON'S FIGURE 19
}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{figures/MBTI_v_time_plot.pdf}
\caption{\label{fig:compare_burned}
Plot of estimated mass burned to IGEs vs.\ time showing the evolution
for both suites of simulations. Results from C-O-Ne progenitors are
in red and C-O progenitors blue.
Note that one of the C/O simulations presented did not complete.
%SAME AS DON'S FIGURE 20
}
\end{figure}
